Simulations log

### 2020-04-10 simulation_study/simulation/README.Rmd
Fix bug C-parameter SCTD config files

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lcdt.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c("7883218", "7883219", "7883220", "7883221", "7883223", "7883224",
                     "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")
```

>>>>

#### RCTD, LCTD
```{r}
rctd_lctd <- createLines(condition[c(2,4)], d=d, hp = "one")
write.table(rctd_lctd, file = "scripts/one/rctd_lctd.txt", sep = "\t", quote = FALSE,
            row.names = FALSE)
#one_rctd_virus etc 
names(rctd_lctd) <- c("7949940", "7949952", "7949953", "7949954", "7949956", "7949959",
                     "7883228", "7883229", "7883231", "7883233", "7883234", "7883236")
```
